Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-06-06 manuscript/manuscript.Rmd
new text in intro and new render

In the summer of 2014, the city of Toledo, OH was forced to shut down their municipal water supply due in part to an excess of Microcystin-LR that resulted from a ongoin harmful algal bloom in Lake Erie.  Since this event, signficant legislation has been passed in the United States and the US Environmental Protection Agency has released suggested microcystin-LR concentrations that would trigger health advisories.

MC requires lab work

MC associated with Chl a

>>>>

In the summer of 2014, the city of Toledo, OH was forced to shut down their municipal water supply due in part to an excess of Microcystin-LR that resulted from a ongoin harmful algal bloom in Lake Erie.  Since this event, signficant legislation has been passed in the United States and the US Environmental Protection Agency (USEPA) has released suggested microcystin-LR concentrations that would trigger health advisories.  While these levels and association advisories are likey to help mitigate the impacts from harmful algal blooms, they are not without complications.  One of these complications is that they rely on availble measurments of Microcysin-LR which requires taking regular water samples and having those samples process in a lab to determin the toxin concentration.  This has the potentially to be costly and time consuming both factors which could limit monitoring efforts.  Fortunately, microcystin-LR has been shown to be associated with several other, more easily measured components of water quality.

Chlorophyll *a* is one of the most commonly measured components of water quality that is also known to be strongly associated with Microsystin-LR concentrations [REFS].

MC associated with Chl a
These levels, along with the existing World Health Organization (WHO) levels represent a range concentrations that occur

### 2015-06-06 manuscript/manuscript.tex
new text in intro and new render

In the summer of 2014, the city of Toledo, OH was forced to shut down
their municipal water supply due in part to an excess of Microcystin-LR
that resulted from a ongoin harmful algal bloom in Lake Erie. Since this
event, signficant legislation has been passed in the United States and
the US Environmental Protection Agency has released suggested
microcystin-LR concentrations that would trigger health advisories.

MC requires lab work

MC associated with Chl a

>>>>

In the summer of 2014, the city of Toledo, OH was forced to shut down
their municipal water supply due in part to an excess of Microcystin-LR
that resulted from a ongoin harmful algal bloom in Lake Erie. Since this
event, signficant legislation has been passed in the United States and
the US Environmental Protection Agency (USEPA) has released suggested
microcystin-LR concentrations that would trigger health advisories.
While these levels and association advisories are likey to help mitigate
the impacts from harmful algal blooms, they are not without
complications. One of these complications is that they rely on availble
measurments of Microcysin-LR which requires taking regular water samples
and having those samples process in a lab to determin the toxin
concentration. This has the potentially to be costly and time consuming
both factors which could limit monitoring efforts. Fortunately,
microcystin-LR has been shown to be associated with several other, more
easily measured components of water quality.

Chlorophyll \emph{a} is one of the most commonly measured components of
water quality that is also known to be strongly associated with
Microsystin-LR concentrations {[}REFS{]}.

MC associated with Chl a These levels, along with the existing World
Health Organization (WHO) levels represent a range concentrations that
occur
